Current State of Knowledge Representation Systems for Robotics

### 2011-11-25 krs-survey.tex
Changed layout to 2 columns
Merged the 'representation of change' paragraph with non-monotonic reasoning

%\documentclass[twoside,a4paper]{report}
\documentclass[a4paper]{article}

@@

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage[draft]{fixme}

@@

@@

\paragraph{Representation of change}

E.g. \emph{"The pancake dough disappears into a pancake"}

@@

\emph{Presupposition accomodation} is the ability to acquire and represent facts that are not
grounded into perception. A typical example is a human telling the robot that
\emph{"there is big blue sphere behind you!"}.

@@

@@

\subsubsection{Knowledge acquisition}
\label{sect|knowledge-acquisition}

\subsubsection{Ability to merge modalities}
\label{sect|modalities-merging}

\subsection{Integration in a larger robotic architecture}
\label{sect|integration-robot}

@@

\begin{tabular}{ll}
\hiderowcolors
{\bf Project} & {\bf Common-sense knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
DY-KNOW & \\
OMKRF & \\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg (Osnabrück) & \\
(DFKI Bremen) & \\
(JSK) & \\

>>>>

%\documentclass[twoside,a4paper]{report}
\documentclass[a4paper, twocolumn]{article}

@@

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage[draft]{fixme}
\fxsetup{footnote}
\fxsetup{nomargin}

@@

Another important application of non-monotonic reasoning is representation of
change: for example, to make an omelette, you need to crack eggs and wipe them.
The eggs disappear and are replaced by an omelette:

$Egg(a) \wedge Egg(b) \wedge MakeOmelette(a, b, c) \to \lnot Egg(a) \wedge
\lnot Egg(b) \wedge Omelette(c)$

The insertion of the proposition $MakeOmelette(a, b, c)$ leads to retraction of
other facts. This rule requires non-monotonic reasoning to be applied.

@@

@@

@@

\subsubsection{Knowledge acquisition and modalities merging}
\label{sect|knowledge-acquisition}

\emph{Presupposition accomodation} is the ability for the system to
automatically create a context allowing to make sense of a proposition.

For instance, we can imagine a human telling a robot \emph{Please get me the
bottle that is behind you}. If the robot has not yet see what is behind it, it
needs to assume (and represents in its knowledge model) that a undefined bottle
can be found somewhere in the half of space behind it.

A knowledge representation system able to copte with presupposition
accomodation would be able to take into account this (usually under-defined)
information that is not grounded into perception for later inferences.

This ability to imagine a physically state of the world that is not actually
perceived can be seen as the converse of the grounding ability.

Note also that presupposition accomodation implies a bidirectional link of the
symbolic knowledge model with a geometric (or physical) model of the
environment. This article focuses on symbolic knowledge representation systems,
but we shall mention when a KRS explicitely provides support for presupposition
accomodation.

%%%%%
\subsection{Integration in robotic architectures}
\label{sect|integration-robot}

@@

@@

\begin{tabular}{lp{4cm}}
\hiderowcolors
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
DY-KNOW & \\
OMKRF & \\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg (Osnabrück) & \\
(DFKI Bremen) & \\
(JSK) & \\
